### 2018-03-08 README.Rmd

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/infer)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

>>>>

<!--figs/infer.svg-->
<!--http://www.r-pkg.org/badges/version/infer-->
<!--figs/master.svg-->
<!--https://img.shields.io/codecov/c/github/andrewpbray/infer/master.svg-->

[![CRAN_Status_Badge](figs/infer.svg)](https://cran.r-project.org/package=infer) [![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer) [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/andrewpbray/infer?branch=master&svg=true)](https://ci.appveyor.com/project/andrewpbray/infer) [![Coverage Status](figs/master.svg)](https://codecov.io/github/andrewpbray/infer/?branch=master)

@@

To install the cutting edge version of `infer` (do so at your own risk), make sure to install `remotes` first:

```{r}
install.packages("remotes")
remotes::install_github("andrewpbray/infer", ref = "develop")
```

To see the things we are working on with the package as vignettes/Articles, check out 
the developmental `pkgdown` site at <https://infer-dev.netlify.com>.

### Contributing

We welcome others helping us make this package as user friendly and efficient as possible. Please review
our [contributing](CONTRIBUTING.md) and [conduct](CONDUCT.md) guidelines. Of particular interest is
helping us to write `testthat` tests and help us in building vignettes that show how to (and how NOT to)
use the package.
